Modern Graph Generators: A Survey

### 2018-10-08 comparison.tex
Cirrection of formats for GraphGen and graphGen

\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2.2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{1.4cm} | l | }

@@

  & GraphGen & -- & -- & Y & N & Y& user-defined  & JSON & N   \\

@@

  & graphGen & pattern-driven & user-defined  & -- & -- & Y & -- &  property graphs & N   \\

>>>>

\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }

@@

  & GraphGen & -- & -- & Y & N & Y& user-defined  & node/edge-list & N   \\

@@

  & graphGen & pattern-driven & user-defined  & -- & -- & Y & -- &  GraphJson, CypherQueries & N   \\

### 2018-10-08 generators_general.tex
Cirrection of formats for GraphGen and graphGen

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called
GraphGen~\footnote{https://www.cse.ust.hk/graphgen/}. It is
based on the IBM synthetic data generation code for associations and sequential
patterns\footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
connected graphs which focuses on the performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes and a list of edges.

>>>>

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called
GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It is
based on the IBM synthetic data generation code for associations and sequential
patterns\footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
connected graphs which focuses on the performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes and a list of edges.
